---
title: "TPP_Fish29"
author: "Madhu"
date: "20 7 2021"
output:
  word_document: default
  html_document: default
---
This test run was to evalute efficiancy inhouse machine for food safety proteomics.
Insect samples from 2019 were used in this study and outcome was copare with the same data. 
libraries 
```{r}
library(PTXQC) # MQ QC
library(XML)
library(tidyverse) # Data handling
library(PTXQC) # MQ QC
library(dplyr)
library(tidyr)
library(ggplot2)
#library(proteus) # MQ statistics
```
# Download the fasta files.

#Comet search 
For running search for each species FASTA file will change but paramet
```{r}
COMET_PARAMETERS <- 'D:/params/comet.params'
FASTA_FILE <- 'D:/Spectral_library/fish_library/probe_fish29/FASTA/uniprot-UP000000437_2-2022.11.18.fasta'
```
## Perform database search
Here we simply call the defined search engine with the defined parameters on each data file separately.
```{r}
mzML_files <- "D:/Spectral_library/fish_library/probe_fish29/mzML"
mzML_list <- dir(mzML_files, full.names = TRUE)
for(x in mzML_list) system(paste('comet', ' -P', COMET_PARAMETERS, ' -N', sub('\\.mzML$',
                                  '', x), ' -D', FASTA_FILE, ' ', x, sep = ''))
```
## Run peptide prophet and protein prophet in gui
##  ProteinProphet results
```{r}
ProteinProphet<-"D:/Spectral_library/fish_library/probe_fish29/mzML"
ProteinProphet_files <- dir(ProteinProphet, full.names = TRUE, pattern = "prot.xml$")
#For merging and modifying the data
protein <- c()
for(x in ProteinProphet_files) 
  {
   doc <- xmlToList(x)
   for (i in seq(3,length(doc)-1)) protein <- c(protein,doc[i]$protein_group$protein$.attrs['protein_name'])
 }
protein <- unique(protein)                                # protein is now a vector of all proteoforms
probability <- list()
for(x in ProteinProphet_files) 
  {
  doc <- xmlToList(x)
  for (p in protein) probability[[x]][[p]] <- 0.9
  for (i in seq(3,length(doc)-1)) probability[[x]][[doc[i]$protein_group$protein$.attrs['protein_name']]] <- doc[i]$protein_group$protein$.attrs['probability']
 }
# For creating matrix for data
DF <- as.data.frame(sapply(probability, rbind), rownames <- protein)
DM <- as.matrix(DF[,1:33])
```
## modify code
```{r}
require(devtools)
df <- apply(DF,2,as.character)
write.csv2(df,"D:/Spectral_library/fish_library/probe_fish29/fish_29.csv", row.names = protein, col.names = TRUE)
```
## For protein description 
```{r}
ProteinProphet<-"D:/Spectral_library/fish_library/probe_fish29/mzML"
ProteinProphet_files <- dir(ProteinProphet, full.names = TRUE, pattern = "prot.xml$")
#For merging and modifying the data
protein <- c()
for(x in ProteinProphet_files) 
  {
   doc <- xmlToList(x)
   for (i in seq(3,length(doc)-1)) protein <- c(protein,doc[i]$protein_group$protein$annotation['protein_description'])
 }
protein <- unique(protein)                                # protein is now a vector of all proteoforms
probability <- list()
for(x in ProteinProphet_files) 
  {
  doc <- xmlToList(x)
  for (p in protein) probability[[x]][[p]] <- 0
  for (i in seq(3,length(doc)-1)) probability[[x]][[doc[i]$protein_group$protein$annotation['protein_description']]] <- doc[i]$protein_group$protein$.attrs['probability']
 }
# For creating matrix for data
DF1 <- as.data.frame(sapply(probability, rbind), rownames <- protein)
DM1 <- as.matrix(DF[,1:19])
```
## modify code
```{r}
require(devtools)
df1 <- apply(DF1,2,as.character)
write.csv2(df1,"D:/Spectral_library/2021_insect_library/out_inhouse/mzML/insect2.csv", row.names = protein, col.names = TRUE)
```

#Heatmap mapping 
For renaming the coulmns with sample names
```{r}
View(df)
hmap<-read.csv2(file = 'D:/Spectral_library/fish_library/probe_fish29/fish_29.csv', header = TRUE)
colnames(hmap)[1]<-"protein"
na1<-"D..Spectral_library.fish_library.probe_fish29.mzML.interact."
na2<-".prot.xml"
a<-str_remove(colnames(hmap), na1)
b<-str_remove(colnames(hmap), na2)
colnames(hmap)<-a
colnames(hmap)<-b
fishname <-read.delim2(file = 'D:/Spectral_library/fish_library/probe_fish29/fishnames.txt',header = FALSE, sep = "\t")
colnames(hmap[2:34])<- fishname$V2
a<-fishname$V2
colnames(hmap)<-c("Protein","Gadus_morhua","Merluccius_merluccius","Pollachius_virens","Melanogrammus_aeglefinus", "Pollachius_pollachius","Molva_molva","Trisopterus_minutus","Trisopterus_esmarkii","Micromesistius_poutassou","Gadiculus_argenteus","Clupea_harengus","Scomber_scombrus","Trachurus_trachurus","Microstomus_kitt","Pleuronectes_platessa","Limanda_limanda","Lepidorhombus_whiffiagonis","Scophthalmus_maximus","Cyclopterus_lumpus","Maurolicus_muelleri","Ammodytes_marinus","Anarhichas_lupus","Argentina_sphyraena","Squalus_acanthias","Amblyraja_radiata","Callionymus_lyra","Argentina_silus","Merlangius_merlangus","Eutrigla_gurnardus")
write.csv2(hmap,"D:/Spectral_library/fish_library/probe_fish29/renamedfish_29.csv")
```

